\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage[hidelinks=true]{hyperref}
\usepackage[usenames, dvipsnames]{color}

\title{SE 3XA3: Development Plan\\GrateBox}

\author{Team 8, Grate
		\\ Kelvin Lin (linkk4)
		\\ Eric Chaput (chaputem)
		\\ Jin Liu (liu456)
}

\date{}

\input{../Comments}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 26, 2016 & Eric Chaput & Created Draft 1\\
September 27, 2016 & Kelvin Lin & Modified Team Meeting Plan for Draft 2\\
September 28, 2016 & Kelvin Lin & Added Team Member Roles for Draft 2\\
September 28, 2016 & Kelvin Lin & Added Git Workflow Plan for Draft 2\\
September 29, 2016 & Eric Chaput & Added to Sections 3,6, and 7\\
September 30, 2016 & Kelvin Lin, Eric Chaput, Jin Liu & Spelling and Grammar 
edits\\
November 4, 2016 & Eric Chaput & Revisions based on TA comments\\
December 6, 2016 & Kelvin Lin & Added Reflection\\
December 7, 2016 & Eric Chaput & Final Edits for Revision 1\\
December 8, 2016 & Kelvin Lin & Edited all spelling and grammar mistakes\\
December 8, 2016 & Kelvin Lin & Reflected new changes in Royal Purple\\
December 8, 2016 & Kelvin Lin & Depreciated all invalid paragraphs\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

\textcolor{RoyalPurple}{Royal Purple text denote changes made for revision 1.}

\section{Abstract}

Having stated the problem to be solved in the problem statement document, Grate 
will develop the Genetic Cars project to solve it. The following document 
details the development plan for Grate's Genetic Cars project.

\section{Team Meeting Plan}

\subsection{Overview}
Grate's meetings will resemble a modified version of daily scrum meetings; 
however, instead of holding daily scrum meetings, they will be held weekly. 
Grate will structure 3 meetings each week, with the first meeting requiring full 
attendance of all members, and the remaining 2 requiring members to attend as 
needed. The first meeting will resemble the daily scrum meeting, while the 
latter two meetings will resolve issues and difficulties mentioned in the former 
meeting.

\subsection{Meeting Structure}
Team meetings will be held three times per week: on Monday from 7:00PM to 
8:00PM, on Wednesday from 8:30AM to 10:30AM, and on Fridays from 2:30PM to 
4:30PM. On Mondays, the team meetings will be held in a meeting room at McMaster 
University. Kelvin Lin will be responsible for booking the meeting rooms, and 
releasing the meeting location 1 week before the meeting date. The meetings on 
Wednesday and Friday will be held in ITB 236.

The meetings on Mondays will be used to aggregate the achievements and 
difficulties of the previous week, and to plan for the upcoming week. Members 
will be presented with the opportunity to discuss any achievements and 
difficulties they encountered while working on their tasks. A list of 
difficulties will be created; however, there will not be an in-depth 
investigation or 
resolution of the aforementioned difficulty. For each issue mentioned, a list of 
team members who are qualified to solve the problem will be created, and a 
member from that list will be chosen to investigate that problem. A meeting will 
be held on the subsequent Wednesday or Friday in order to discuss the resolution 
or further issues pertaining to that problem. The meetings on Monday will 
conclude with a list of tasks each member is responsible for in the upcoming 
week.

The meetings on Wednesdays and Fridays will be used to address specific 
decisions pertaining to the project deliverables. Topics will include making 
specific design decisions, resolving issues mentioned on Monday's meeting, 
resolving any issues discovered throughout the week, and addressing any 
intergroup problems. To account for in-lab activities, the meetings will be 
divided into sub-meetings, and members will only be required to attend meetings 
that concern aspects of the tasks that they are working on. Members can work on 
the in-lab activities when they are not in a meeting. 

\subsection{Components of Meetings}
Key components of team meetings include the chair, the agenda, the scribe, and 
the meeting minutes.

\subsubsection{The Chair}
The chair will be responsible for organizing the topics to be discussed at the 
meeting and orchestrating the flow of the meeting. Before each meeting, the 
chair is responsible for creating an agenda for the meeting. During the 
meetings, the chair has an obligation to maintain a neutral front; the chair 
exert his authority to favour one side of an issue over the other side of the 
issue. However, the chair will have the authority to defer topics that threaten 
the overall structure of the meeting: if a topic exceeds the allotted time for 
discussion or if an unforeseen issue arises from a predetermined topic, the 
chair has the authority to defer the topic to a future meeting. The chair will 
not have the authority to veto decisions made by the team, nor will the chair's 
opinion be valued more than the other members. At the end of each meeting, the 
chair is responsible for establishing the next meeting date and making the 
appropriate reservations for a meeting space. Unless otherwise noted, Kelvin Lin 
will be the chair of the meetings.


\subsection{Emergency Provisions}
In the unlikely event of an emergency, impromptu meetings can be held on 
Thursdays 12:30PM to 1:30PM, at a location to be determined. All members are 
expected to be present at emergency meetings. Depending on the urgency of the 
meeting, an agenda for the meeting may not exist; however, the scribe will still 
be responsible for taking notes and releasing meeting minutes after the meeting. 
Topics at emergency meetings will only pertain to issues at-hand: that is, no 
long-term planning will be done at emergency meetings unless otherwise required 
by the deliverable. If required, additional meetings can be scheduled through 
the Facebook Messenger platform on an as-needed basis.

\section{Team Communication Plan}
\subsection{Online Platforms}
Grate will communicate with a variety of online platforms and in-person 
meetings. While the structure of in-person meetings is described above, the 
online platforms used include Facebook, GitLab, and Telephone/Internet Phone.

\subsubsection{Facebook}
Facebook offers an instant messaging service called Messenger, which will serve 
as the team's primary form of online communication. Facebook offers message 
logging, real-time communication, and private messaging, all of which are 
convenient features for the team. All message logs are recorded by Facebook, 
which can be referenced in the future. Moreover, Facebook messages are delivered 
in real time, so members can stay updated on the status of the project. Private 
messaging will also allow members to discuss aspects of the project that would 
not interest the third member.

\subsubsection{GitLab}
GitLab is a repository management system that allows users to version their 
code. Grate will use GitLab to store the project and any relevant 
documentation. GitLab will be used because it provides a form of separation of 
concerns for each member, while allowing for concurrent access to the code. 
Members can add to the code repository without interference from other updates. 
GitLab also allows members to have local copies of the code for experimentation. 
Accordingly, GitLab will be used to manage documents used by Grate.

\subsubsection{Phone}
The phone provides real-time voice-to-voice communication between members. The 
phone will be used for emergency contact purposes. Such emergencies include 
power outages, last minute changes in plans, and last minute technical errors. 
The phone will be used for emergency purposes because it provides synchronized 
communication between the members: the communicating members are expected to 
respond as soon as communication ends from the other member.

\section{Team Member Roles}
Grate will have the following roles: team lead, technology expert, graphics 
expert, theory expert, qualitative testing expert, and quantitative testing 
expert. The assignment and descriptions of each role follow.

\subsection{Assignment of Roles}
The following table shows the assignment of roles in Grate.

%Table generated with: http://www.tablesgenerator.com/#
\begin{table}[h!]
	\begin{tabular}{ll}
		Team Member & Role                                        \\
		Kelvin Lin  & Team Lead, Technology Expert                \\
		Eric Chaput & Theory Expert, Qualitative Testing Expert  \\
		Jin Liu     & Graphics Expert, Quantitative Testing Expert
	\end{tabular}

	\caption{Grate Role Assignments}
\end{table}

\subsection{Description of Roles}

\subsubsection{Team Lead}
The team lead is responsible for the overall management of the project. The team 
lead is responsible for ensuring that all deliverables are made to 
specification and on time. To accomplish this, the team lead must be sensitive 
to the member's skills and abilities, and partition tasks to allow all of the 
other members to succeed and to develop new skills. The team lead shall ensure 
that every member is aware of the tasks that need to be done, and what their 
role is on the team. The team lead is also responsible for facilitating 
communication to external parties by representing the voice of the team.

\subsubsection{Technology Expert}
The technology expert is responsible for maintaining current knowledge on 
general aspects of the technology used. The technology expert will serve as the 
first point of contact for any technical problems encountered with, but not 
limited to, Git, HTML5, JavaScript, \LaTeX, GanttProject, Doxygen, and Karma. 
The technology expert will be in charge of general troubleshooting, and he will 
redirect members to the appropriate experts when required. Moreover, the 
technology expert will be responsible for researching new technologies that can 
be used for the project.

\subsubsection{Graphics Expert}
The graphics expert is responsible for maintaining current knowledge on the 
algorithms and technology needed to implement the graphics for the project. The 
graphics expert shall learn all tools necessary in order to create a graphical 
interface for the project, and he will be responsible for communicating this 
knowledge to other members of the team in a manner comprehensible by both 
members with and without prior technical knowledge. The graphics expert will 
also be responsible for experimenting with new graphical technologies, and 
spearheading the graphics-related implementation initiatives of the project. 

\subsubsection{Theory Expert}
The theory expert will be responsible for maintaining current knowledge of the 
theory needed to comprehend the algorithms used in the project. The theory 
expert will be responsible for understanding theory behind the physics, learning 
algorithm, and graphics. The theory expert will be responsible for finding any 
references to published text when needed. Moreover, the theory expert will be 
responsible for communicating this knowledge to other members of the team in a 
manner comprehensible by both members with and without prior technical 
knowledge.

\subsubsection{Qualitative Testing Expert}
The qualitative testing expert will be responsible for maintaining current 
knowledge of qualitative testing methodologies within the scope of the project. 
The qualitative testing expert will be responsible for leading any qualitative 
tests including but not limited to market research and observation, in-person 
and online surveys, discussion/focus groups, and code review sessions. Such 
tasks may involve partitioning tasks for each initiative and assigning the tasks 
to the 
appropriate member. Moreover, the qualitative testing expert will be responsible 
for reporting any results to the group and making recommendations based on the 
results to improve the projects.

\subsubsection{Quantitative Testing Expert}
The quantitative testing expert will be responsible for maintaining current 
knowledge of quantitative testing methodologies within the scope of the project. 
Before the implementation of the project, the quantitative testing expert shall 
familiarize himself with different tools used to test the agreed-upon 
technologies. The quantitative testing expert will be responsible for leading 
any quantitative testing initiatives including unit testing, integration 
testing, system testing, automated testing, and manual testing. Such tasks may 
involve partitioning tasks for each initiative and assigning the tasks to the 
appropriate member. Moreover, the quantitative testing expert will be 
responsible for reporting any results to the group and making recommendations 
based on the results to improve the project.

\section{Git Workflow Plan}
Grate will utilize a feature-branch workflow plan. 

\subsection{Feature-branch Overview}
The feature-branch workflow branch is a Git workflow plan that utilizes 
different branches to implement different feature of the programs. Once a 
particular feature of the program is completed, its branch will be merged with 
the master branch. Labels will be used to tag submission files, while milestones 
will be used in order to signal any major revisions on the master branch.

\subsection{Rationale}
In selecting a Git workflow plan, Grate wanted a workflow that would provide 
maximum support for separation of concerns, while guaranteeing that there will 
always be a working version of the project easily assessable. Such workflow 
would simplify both the development, testing, and deployment efforts of the 
team. A high level of separations of concerns would allow multiple members to 
code concurrently without interference from code changes from other members. 
Members can also test their code using the master branch as a driver. This is a 
valid approach as any functional code on the master branch would have already 
been tested. The second requirement of the Team's desired workflow plan 
guarantees this by specifying that only functional versions of the project are 
to be committed to the master branch. 

The feature-branch workflow plan fully satisfies the requirements mentioned 
above. It supports separation of concerns by placing each feature of the program 
on a separate branch. Each branch will stem from a node on the master branch, 
allowing each branch to have an independent copy of the previously functional 
code. This will allow members to write new features in isolation, without having 
to account for continuous changes made by other members. The master branch can 
also serve as a driver for unit testing, and for regression testing. 
Accordingly, the feature-branch workflow was chosen.

\section{Proof of Concept Demonstration Plan}
The proof of concept demonstration will consist of three independent components 
that resemble simplified versions of the final product: the car model, the 
genetic algorithm (GA) module, and the graphics simulation. 

\subsection{The Car Model}
The Car Model will be a JavaScript module that demonstrates two things: the car 
is representable as a data structure, and the Box2D API can be integrated into 
the project. 

\subsubsection{The Car}
The car in this project is composed of 8 vectors attached to a central point. 
The 
tips of the vectors are connected to form triangles. Each car contains 8 
vectors. In addition, each car can have up to \textcolor{RoyalPurple}{2} wheels. Each wheel has a radius, 
an axle angle, and a vertex. Two wheels can lie on the same vertex. Each car 
will also have mass, which will be a randomly generated value between two 
predetermined numbers.

\subsubsection{The Deliverable}
The Car Model will modelled with a \textcolor{RoyalPurple}{JavaScript prototype object} with properties such as the coordinates for each of its 8 vectors; 
the vertex, axle angle, and radius of each of its 8 wheels; a boolean for each 
of its wheels to indicate whether the wheel exists. A script to test the \textcolor{RoyalPurple}{Car Object}
model will also be created. This script will access each field of the car and 
output its value in text to the console. The script will also use the Box2D API 
to create the corresponding vectors for the car, and if it is successful, then 
it will print "true" to the console.

\subsubsection{The Risks}
The Box2D API poses the most significant risk for the car model. The Box2D API 
defines the car entity in terms that can be used with many physics equations, 
which is important for calculating the fitness function of the car. In the event 
that the Box2D API \textcolor{RoyalPurple}{proves} to be infeasible for Grate, alternate \textcolor{RoyalPurple}{arrangements}
will have to be made in order to complete the project: the team will resort to 
using basic kinematics equations to calculate the fitness function instead of 
using the API. A possible drawback to this approach would be that the members of 
Grate is generally unfamiliar with Newtonian mechanics, so external assistance 
would be required. Tentatively, the team plans to consult with Dr. Spencer Smith 
during his office hours should this assistance be required.

\subsection{The Genetic Algorithm}
The purpose for implementing the GA is to demonstrate its practicality to 
the project. In order for this portion to succeed, it must be able to select for 
the top n cars given an array of cars, n, and fitness scores as input; crossover 
the genes of these cars; and mutate the genes of the offspring.

\subsubsection{Genetic Algorithm Overview}
GAs attempt to find near-optimal solutions to problems with incomplete or 
imperfect information by emulating the process of natural solution. In this 
project, the GA will be used in order to find the best car in terms of the 
distance driven on an predetermined road. First, the GA will select for the top 
n cars based on their fitness scores. Then, the GA will use the fields of the 
car as genes, and swapping them in order to simulate reproduction. This project 
will do this by randomly selecting two fields and two cars, and swapping those 
two fields such that the first car will have the two fields from the second car 
and the second car will have two fields from the first car. Finally, to finish 
creating the offspring, the GA will randomly change some of the fields at a 
frequency based on a mutation likelihood between 0\% and 100\%. 

\subsubsection{The Deliverable}
The deliverable will consist of a JavaScript file that consists of at least 
three functions: selectNextGeneration(cars:Car[], fitnessScores: Integer, n: 
Integer), crossoverOffsprings(cars: Car[], population: Integer, n:Integer), and 
mutateOffsprings(cars: Car[], mutationFactor: Integer, n: Integer). The 
selectNextGeneration function will take an array of cars and their fitness 
scores, and return an array containing the top n cars. The crossoverOffsprings 
function will take an array of cars, and randomly select parent cars (from the 
first n element in the cars array) to cross over their genes, such that the 
number of cars in the cars array equals the population. The mutateOffsprings 
function will randomly mutate the fields of the offspring by a given mutation 
factor.

This file will be demonstrated using another script with hardcoded values for 
cars. The script will first run the selectNextGeneration function, and print the 
fields of the top n cars to the console. Then, the script will crossover the top 
n cars using the crossoverOffsprings function, and print their fields to the 
console, as well as which fields and cars were used to make the swap. Finally, 
the mutateOffsprings method will be used to mutate the cars and then the fields 
of the cars that mutated as well as their previous fields on separate lines.

\subsubsection{The Risks}
The adaptation of algorithm itself presents a significant risk for this project. 
Any assumptions made in the original algorithm will carry over to the project 
where those assumptions may not hold to be true.  \textcolor{RoyalPurple}{Furthermore}, if any errors 
exist in the GA code, the final result will be negatively effected. To avoid 
this risk, the original algorithm will be tested in an isolated \textcolor{RoyalPurple}{environment} to 
ensure its general accuracy. The coded algorithm will also be tested in 
isolation of the program's other components to ensure it is properly implemented 
in JavaScript. This is feasible due to \textcolor{RoyalPurple}{Grate's} object oriented programming 
approach to this project.

\subsection{The Graphics}
The purpose of the graphics demonstration is to show competency in the 
technologies required to create the graphical interface for the project. The 
final deliverable will consist of a simple 3-vector car moving horizontally 
across the screen over a dynamically generated road, with a camera centred on 
the car.

\subsubsection{Graphics Overview}
The graphics for this project consists of multiple cars displayed on the screen, 
moving horizontally over a road, with the camera focused on the fastest car in 
the population. The user interface also allows users to modify certain 
parameters of the GA, and view the improvement of the cars over several 
generations. 

\subsubsection{The Deliverable}
The deliverable for the proof of concept demonstration will be a simplified 
version of the final user interface. It will consist of a HTML5 canvas with a 
dynamically generated line representing the road near the bottom of the canvas. 
A random car will be generated with \textcolor{RoyalPurple}{8} vectors and 2 wheels (2 
circles). The car will move horizontally across the screen indefinitely. A 
camera will also focus on the car, so that the center of the car will always be 
at the center of the screen.

\subsubsection{The Risks}
The implementation of the JavaScript graphics language will present a 
significant risk for this project. Grate has more experience with C++ and Java 
graphics packages, and it is possible that the adaptation of JavaScript will 
prove more difficult then initially believed. \textcolor{RoyalPurple}{Grate's} graphics and technology 
experts have arranged to minimize this risk by educating themselves on 
JavaScript's graphics functionality extensively through online resources and 
peers familiar with JavaScript.

\section{Technology}

This project will use technology that all group members are already familiar 
with on a basic level. The project itself will be coded in Java Script, however 
all group members understand that Java may be used if JavaScript proves too 
difficult to use for this project. All group members are familiar with both of 
these languages and no further learning will be required. \textcolor{RoyalPurple}{Grate's} graphics 
expert is also adept at creating graphics in JavaScript. Written reports and 
documents will be generated through Latex, a technology being taught in the 3XA3 
course, and documents and reports will be shared through Git, another technology taught in the 3XA3 course. The technology expert will ensure that all 
group members are aware of how to use these technologies. Testing will be aided 
by the use of Java’s built in unit test functionality. Dox will serve as the 
primary document generator, and QUnit will serve as the means of automated 
testing.

\subsection{JavaScript}

JavaScript as a programming language is used for web applications. JavaScript is 
the ideal programming language for this project. Member's of Grate is familiar 
with JavaScript, and \textcolor{RoyalPurple}{Grate's} graphics 
expert believes that JavScript will work best for his role. The final project 
will also closely 
resemble a standard web page in design. Finally, since the original basis for 
the 
project is also written in JavaScript, the original source code code can be more 
easily used for 
inspiration and troubleshooting.

\subsection{\LaTeX}

\LaTeX will be used to generate documents for this project. \LaTeX's ability for 
multiple team members to effect changes simultaneously and its versatility 
across platforms makes it ideal for this project. As of September 28 2016 all 
team members have acquired a working knowledge of how \LaTeX functions, and it 
is 
believed that no further education will be required. If any such education is 
necessary the TAs and the Latex tutorial found online will be \textcolor{RoyalPurple}{Grate's} go-to 
instructors. 

\subsection{GitLab}

GitLab will be used to share and store documents for this project. More 
information on GitLab and how it will be used for this project can be found in 
sections 2.1.2 and in the Git Workflow Plan found in section 4. All Grate 
members are familiar with GitLab and how it functions. 

\subsection{JSDoc}
\textcolor{RoyalPurple}{JSDoc will be used to generate documents. JSDoc is a JavaScript documentation 
generator ran through the command line. It uses a similar commenting syntax to JavaDocs, and it supports additional tags that allows it to create more detailed specifications for the project. Its well documented nature 
makes it a good choice for this project. A link to JSDoc can be found at
\url{http://usejsdoc.org/}.}

\subsection{QUnit}
QUnit will be used for automated testing for this project. Its similarity to 
JUnit, an automated testing software for Java, means that it will be easy to 
learn, and its cross platform flexibility means that it is unlikely to cause 
technical problems. The original source of QUnit can be found at
\url{https://qunitjs.com/}{https://gunitjs.com}

\subsection{Bootstrap}
\textcolor{RoyalPurple}{
Bootstrap is an HTML add-on that allows users to build custom websites following a predefined theme. Bootstrap allows users to quickly make simple, yet elegant responsive websites that scale to any resolution. Boostrap will be used in order to build the website for this application because it is completely open source, and it is thoroughly documented. A link to Bootstrap can be found at \url{http://getbootstrap.com/}.}

\subsection{JQuery}
\textcolor{RoyalPurple}{
JQuery is a JavaScript API that allows users to interface with interactive elements of an HTML page easily. JQuery will be used in order to get input from the user, as well as to get the dimensions of the user's screen. JQuery is easy to learn, and it is thoroughly documented. A link to JQuery can be found at \url{https://jquery.com/}.}

\section{Coding Style}

Code will be styled primarily as has been taught by the software engineering 
program at McMaster University. \textcolor{RoyalPurple}{Grate} will undertake an object oriented 
programming approach to achieve maximum modularity and information hiding. The 
team shall also ensure that the code meets several aesthetic guidelines outlined 
here. All code is to be well commented, with comments being placed before the 
code. Comments are to be written with the understanding that they should be 
concise and easy to comprehend by outside parties. To \textcolor{RoyalPurple}{satisfy} these 
requirements, Mozilla Developer Network's coding style will be adopted by the 
team. 

\subsection{Mozilla Developer Network}

Mozilla Developer Network will be \textcolor{RoyalPurple}{Grate's} default coding style. It contains 
subsections specifically for JavaScript, the programming language of choice for 
this project.  The guidelines for this coding style can be found at
\url{https://developer.mozilla.org/en-US/docs/Mozilla/Developer\_guide/Coding\_Style}.

\section{Project Schedule}
Please find the project schedule at 

\url{https://gitlab.cas.mcmaster.ca/linkk4/GrateBox/tree/master/ProjectSchedule}.

\section{Project Review}
\textcolor{RoyalPurple}{The past four months have been successful for Grate. Grate 
accomplished all of 
the goals it specified in the beginning with a high degree of success. Grate was 
able to re-implement Genetic Cars by rednuht.org while creating extensive 
documentation on the project following standard software engineering 
principles.}

\textcolor{RoyalPurple}{The members of Grate were able to experience first-hand the 
thrills and 
challenges of implementing a medium-scale project, and this experience allowed 
all members to grow in significant ways: both technically and managerially. }

\textcolor{RoyalPurple}{From the beginning, a key lesson Grate learned was to start 
coding early, but 
not become attached to the code that is written. The proof of concept 
demonstration proved effective in showing Grate that proper software design 
techniques need to be used in order to build an extensible system. Initially, 
the proof of concept was built in a cut-and-paste fashion, reusing parts of code 
that achieved some desired function. However, it was through this demonstration 
that Grate realized that it would be extremely challenging to modify this code 
in the future. The proof of concept helped set Grate on a road to using software 
design principles in order to build a strong and understandable system.}

\textcolor{RoyalPurple}{Moreover, creating the different documents for the project 
allowed the members 
of Grate to build a project that is bigger than what any individual member could 
have built. By writing complete and relevant documents, the individual members 
of Grate were able to  communicate asynchronously with other members about the 
tasks that they were working on. This allowed for members to build off on each 
other's code before the other person's code was complete. Of course, this was 
effective partially because of each member's trust in each other, and the common 
desire to succeed and build an amazing product in this course.}

\textcolor{RoyalPurple}{Macroscopically, the iterative process that Grate used was very 
effective in 
developing software project management skills. The Gantt chart was used 
extensively in the software development process as a guideline for each member 
when direction was needed. The use of Gitlab Issue Tracking was also helpful in 
decomposing tasks that each member needed to do, as well as communicating with 
other members about the status of each member's work. The use of version control 
and branching allowed for multiple copies of the project to exist on different 
machines at the same time - members did not have to wait for other members to 
finish their section of the code before starting their own. These tools allowed 
each member of Grate to refine their teamwork, communication, and time 
management skills, which benefited the team as a whole.}

\textcolor{RoyalPurple}{Nevertheless, GrateBox is still in its early stages of 
development, and there 
are still tasks Grate has left incomplete at the time of writing. On the 
technical side, there are several different types of genetic algorithms that 
GrateBox could be made to support. Moreover, support for more parameters can be 
made for the user to customize. }

\textcolor{RoyalPurple}{With respect to software project management, the use of PERT 
charts, agile 
methodology, and continuous integration could be implemented. The use of PERT 
chart would extend the effectiveness of the Gantt chart, so that each member 
knows when they have slack time and when they are on the critical path. Agile 
methodology could perhaps expiate the process of software development through 
more frequent, smaller iterations. Continuous integration would allow the 
software to be tested every time a build is created. By implementing all of 
these features, GrateBox would be a more powerful application to teach students 
and professionals the power of Genetic Algorithms.}

\textcolor{RoyalPurple}{Ultimately, the members of Grate started this project with no 
prior experience 
with software project management. However, after going through several 
iterations of the design process, every member became adept at effectively 
contributing to each step of the process. By using different software management 
tools, GrateBox became what Grate considers a successful application in under 
four months.}

\end{document}

