\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\Genetic Cars}

\author{Team 8, Grate
		\\ Kelvin Lin (linkk4)
		\\ Eric Chaput (chaputem)
		\\ Jin Liu (liu456)
}

\date{}

\input{../Comments}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Sept 22 & Kelvin Lin & Completed fields for names and team information\\
Sept 23 & Kelvin Lin & Created first draft of problem statement\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

Genetic algorithms (GA) are evolutionary metaheuristic algorithms that are used to search for near-optimal solutions to a wide variety of problems with incomplete or imperfect information. Applications of genetic algorithms include automated design, bioinformatics, economics, game theory, and training neural networks. Students and professionals from many different industries, with technical and non-technical backgrounds can benefit from using GA. However, despite the numerous applications of GA, there is a persistent lack of training resources for students and workers to learn about them. 

In an informal survey of online resources conducted by Team 8, it was found that the GA training resources online typically contained one of two flaws: they either assumed that the reader has extensive knowledge in mathematics, or they lacked practical demonstrations to show the power of GA. The former flaw presents GA as a complex tool exclusively used by mathematicians and other mathematically inclined professions. Extensive mathematical jargon may also confuse novice learners who have a weak grasp of mathematical notation and mathematical theorems. Moreover, large mathematical explanations may intimidate some learners, discouraging them from pursuing an otherwise powerful tool for their work. The latter illustrates GA as a narrowly scoped tool used to solve specific problems. It fails to demonstrate the versatility of GA and how GA work to find the near-optimal solutions to problems without a clear optimal solution. Online resources in this category often use simple static examples, which hide the evolution process from the learner. This reduces the learner's appreciation for GA, as they cannot see how the algorithms find the near-optimal solution. The key to learning is also to keep the student engaged in what they are doing and simple static examples make it hard to remain interested in the material.

Ultimately, despite the versatility in using GA to find near-optimal solutions to problems in a variety of different industries, there continues to be a lack of accessible training resources for students and professionals to learn about GA. This leaves many learners discouraged or impartial about the useful about the algorithm. Accordingly, there is a dire need for ways to teach both students and professionals about GA in a manner that is both relevant and applicable to their daily lives.

This project will be undertaken by Team 8 of the 3xa3 class at McMaster University. It will be overseen and ultimately evaluated by Professor Spencer Smith and the staff of McMaster’s 3xa3. The intended final users for this project will be students and others interested in learning about GA, including their uses and functionality. The intended environment for this software would be in the classroom, however our intended user base could also access this online.


\end{document}