\documentclass[12pt, titlepage]{article}

\usepackage{fullpage}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{longtable}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\newcounter{mnum}
\newcommand{\mthemnum}{M\themnum}
\newcommand{\mref}[1]{M\ref{#1}}

\title{SE 3XA3: Test Report\\GrateBox}

\author{Team 8, Grate
		\\ Kelvin Lin (linkk4)
		\\ Eric Chaput (chaputem)
		\\ Jin Liu (liu456)
}

\date{\today}

\input{../Comments}

\begin{document}

\maketitle

\pagenumbering{roman}
\tableofcontents
\listoftables
\listoffigures

\begin{table}[h]
\caption{\bf Revision History}
\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Dec 6 & 1.0 & Document creation\\
Dec 7 & 1.1 & Document completion\\
Dec 8 & 1.2 & Final document edits\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\pagenumbering{arabic}

This document will make frequent reference to the Development, Test Plan, SRS 
and Design documents of the GrateBox project. They can be found 
\href{https://gitlab.cas.mcmaster.ca/linkk4/GrateBox/tree/master/Doc/DevelopmentPlan}{here}, 
\href{https://gitlab.cas.mcmaster.ca/linkk4/GrateBox/tree/master/Doc/TestPlan}{here}, 
\href{https://gitlab.cas.mcmaster.ca/linkk4/GrateBox/tree/master/Doc/SRS}{here}, 
and 
\href{https://gitlab.cas.mcmaster.ca/linkk4/GrateBox/tree/master/Doc/Design}{here} 
respectively.

\section{Functional Requirements Evaluation}

An evaluation of functional requirements reveals near complete coverage by the 
functional test cases. The tests written for GrateBox caught bugs and errors 
that may have gone otherwise unnoticed by the development team. Those will be 
discussed below. Many of the more mundane or generic functional requirements 
were fulfilled well before testing began, so they will not be addressed, as 
their verification would be redundant at this point. \\

Functional requirements are listed by the number given to them in the Software 
Requirements Specification document. Note that these functional requirements are 
laid out in more detail in the SRS document linked above, and it should be 
referred to for further elaboration.\\

\textbf{Requirement \#5/6}: Testing revealed inconsistent masses across similar 
cars in different generations. This was revealed to be a conceptual problem with 
the code. Initially, mass was treated as a fixed value common to all cars. While 
this technically fulfilled the functional requirements for mass, later 
generations would trend towards the extremes of and eventually past the range of 
viable mass values dictated by the requirements. The development team elected to 
remedy this problem by making the mass value of cars a variable dependant on 
density and volume. With a constant density value set across all cars, and a 
much stricter range of possible volumes that cars could possess, mass values in 
test cases after this fix fulfilled these mass requirements far more 
consistently.\\

\textbf{Requirement \#8}: While testing did not reveal a problem with the actual 
display of fitness values required by this requirement, it did reveal a flaw in 
the creation of these values. Initially, the fitness of a car was determined by 
the distance along the x-axis of the road that the car had travelled. This 
solution did not account for vertical displacement, which became ever more 
important as GrateBox incorporated more sloped roads, to the point where many 
cars that were technically travelling a shorter distance along the road were 
receiving higher fitness values, skewing the results and threatening the 
integrity of GrateBox itself. The development team was quick to implement a more 
nuanced fitness algorithm that rated cars off of both their vertical and 
horizontal displacement and also accounted for the lifetime and durability of 
the car.\\

\textbf{Requirement \#10/11}: Whenever the user enters a new value into any of 
the fields that are able to be changed by the user, a new simulation begins with 
those values. While this seemed obvious to the development team, user surveys 
revealed that this process confused users. To this end, the functionality of 
these user changeable fields was updated to require the user to select enter 
following the entrance of a new value into the field. The following user 
feedback revealed that this change in functionality resulted in a better 
product.\\

\textbf{Requirement \#13/14}: Testing revealed that many users felt the need to 
enter impossible values into user changeable variables. For example, many users 
attempted to simulate generations of cars with negative amounts of cars per 
generation. Others simply attempted to enter strings of text into these fields. 
GrateBox, at the time incapable of processing these invalid inputs, failed as a 
result. The development team quickly implemented error messages and try/catch 
exceptions into the code in order to thwart user attempts to circumvent the 
functionality of the program.\\

\textbf{Requirement \#18}: The algorithm that was designed to determine at what 
exact point along the road a car was deemed to be non-moving evolved over the 
course of the testing process. The first set of tests illuminated the need for 
larger health bars for each car to account for some cars stopping temporarily 
along the road as they attempted to circumvent terrain challenges. This was 
followed by a number of bugs in Java's graphics libraries, which caused cars to 
be deemed non-moving far before the graphics indicated this. These bugs were 
eventually ironed out of the program.

\section{Nonfunctional Requirements Evaluation}

An evaluation of non-functional requirements reveals near complete coverage by 
the non-functional test cases. The tests written for GrateBox caught problems 
and  potential improvements in GrateBox that were resolved by the development 
team. Those will be discussed below.\\

Non-functional requirements are listed by the number given to them in the 
Software Requirements Specification document. Note that these non-functional 
requirements are laid out in more detail in the SRS document linked above, and 
it should be referred to for further elaboration. While many non-functional 
requirements required only software test to validate, many required timed tests 
by user volunteers and user feedback collected through surveys. The exact 
details of the survey can be found in the Test Plan document linked at the 
beginning of this document.\\

\subsection{Look and Feel Requirements}

\textbf{Requirement \#21}: The need for GrateBox to be attractive to a student 
audience was of crucial importance to GrateBox's success. Initial releases of 
GrateBox however were met with hostility by users surveyed. To this end, another 
look was taken at technologies necessary to aid in increasing the aesthetic 
appeal of GrateBox. Bootstrap was chosen as a result of this feedback and was 
incorporated into GrateBox. User surveys following the update revealed a marked 
increase in user support of the product's appearance.\\

\textbf{Requirement \#22}: The importance of maintaining an education and 
professional outlook was identified early, and Grate did its utmost to ensure 
that this style was projected by the product, and it was felt that the program 
did in fact project this style during initial releases. While this sentiment was 
shared by most users surveyed, many also recommended that the look and feel of 
GrateBox could be improved by enabling additional options for the user to reduce 
the confusion the original releases could project. In particular, many users 
requested the ability to pause the simulation to allow them to utilise GrateBox 
at their own pace rather than a pace set by the program. With the goal of 
reducing confusion, a pause button was added, along with a clearer input method 
for user changeable parameters 

\subsection{Usability and Humanity Requirements}

\textbf{Requirement \#23}: Being an educational tool, it was of the utmost 
importance that GrateBox be easy to use. To this end, a set of tasks was set 
before users to be completed within a set time frame, to judge the program's 
ease of use. While most users were able to complete the tasks in a timely 
manner, some were not. These users had problems understanding exactly what 
fitness values were in practical terms, and so could not utilize the program to 
the fullest. To remedy this, Grate incorporated a more detailed and nuanced 
explanation of the program's fitness value, and the program's ease of use 
increased greatly as a result.\\

\textbf{Requirement \#24}: If a learning tool is to be successful, it must allow 
for some degree of user engagement, and Grate aimed to accomplish this with 
GrateBox by allowing for a degree of personalization by the user. The mutation 
rate, population size, and number of parents of each set of generations was 
fully customizable by the user from the very earliest releases, however while 
users could update these values and see the changes in the simulations that 
resulted from these updates, many could not grasp exactly what the changes they 
were making were changing in real terms. To this end Grate incorporated written 
explanations of each user changeable field to help the educational process 
GrateBox attempted to induce.\\

\textbf{Requirement \#25}: It was always intended for GrateBox to be composed of 
only a single web page with very simple commands so that even users with no 
experience with the program could operate it. Our testing revealed that users 
were able to easily learn how to use the products minimal functionalities. While 
some users had problems understanding the exact effects of these functionalities 
(see requirements 23 and 24), none were incapable of operating them.

\subsection{Performance Requirements}

\textbf{Requirement \#26}: In order to maintain user attention, the speed of 
GrateBox had to be such that the user would not grow board of waiting for the 
product. Manual testing by the testing team revealed that the program did in 
fact meet or surpass our metrics for speed defined in the requirements, and most 
users surveyed agreed with this assessment. Testing the speed of the program 
however revealed the need to remove a significant amount of useless code from 
the API GrateBox utilized in order to further reduce GrateBox's runtime.\\

\textbf{Requirement \#27}: As a learning tool, GrateBox's precision was of the 
utmost importance. If the user believes that an educational program they are 
using is inaccurate, they will likely doubt the veracity of what is being taught 
to them. To this end, the product was made to display all values to the 
precision outlined in the requirements, however testing demonstrated several 
accuracy errors in final calculations of values. These resulted from the use of 
both integers and floats in the same mathematical equations. These errors were 
fixed in the final product. The actual testing process also revealed the need to 
switch our sorting method from a heap sort to a quick sort, as heap sorting 
methods proved overly difficult to verify with automated testing.

\subsection{Robustness, Maintainability, and Compatibility}

\textbf{Robustness}: While no formal robustness testing was conducted by Grate, 
several informal robustness tests were conducted over the lifetime of the 
development cycle. The most important of these were tests run to simply see how 
many generations GrateBox could run for before encountering errors. Grate was 
very thankful these tests were undertaken, as memory leak issues were 
encountered resulting in the sudden collapse of GrateBox after 4 generations of 
automobiles. The source of these errors was tracked to the API. Following 
extensive modification of elements of GrateBox's API, the program now runs for a 
significant amount of time before encountering problems, long enough that only 
the most dedicated and fanatic of users could possibly encounter them.\\

\textbf{Requirement \#28}: The need for GrateBox to be easy to update and 
upgrade was made clear before Grate even began the development process, as it 
was believed making this a priority early on in the development process would 
make the development process itself all the more easy. Ultimately, informal 
discussions with other software developers and internal testing saw the almost 
absolute removal of constant values in the GrateBox code. These were replaced 
with variable values, greatly adding to GrateBox's longevity as a software 
product.\\

\textbf{Compatibility}: One benefit of programming in such a common language as 
JavaScript was the overwhelming compatibility of the programming language, and 
the use of HTML for the final website design also aided in improving GrateBox's 
compatibility. No compatibility problems were encountered during the testing 
process for and device with JavaScript installed, verifying the fantastic 
compatibility of GrateBox.

\subsection{Legal Requirements}

While no legal requirements existed for this project, as all software utilized 
was fully open sourced, a software license was created by the recommendation of 
a surveyed user to be safe.

\subsection{Health and Safety Requirements}

While no formal health and safety testing was undertaken, as the health and 
safety risks of this project were deemed to be too minimal to warrant such 
testing, users were informally asked throughout the survey process if they had 
concerns regarding the GrateBox project when it came to health and safety. No 
users had any concerns. While no significant health and safety risks could be 
identified, Grate made the effort to identify a set of potential user problems 
given extreme conditions (this list can be seen in section 4.3.3 of the test 
plan).

\section{Comparison to Existing Implementation}

The original implementation contained no testing of its own. This is somewhat 
understandable given the seemingly overnight creation of the original product. 
As such Grate's test cases have nothing to compare to in the original 
implementation. Were there such tests to compare to, Grate would compare the 
coverage, results, and random inputs of the existing implementation's test cases 
to those of Grate. Grate would also search for missing elements of one 
implementation that are present in the other, to see if Grate's implementation 
has missed a crucial component of the existing implementation.\\

One test conducted by Grate (GR-1.1) required a visual comparison to the 
original implementation. This 
comparison helped validate the results of the test. The test in question was 
GR-1.1 on the Test Plan document. 

\section{Unit Testing}

All unit testing for this project can be found in the test folder found 
\href{https://gitlab.cas.mcmaster.ca/linkk4/GrateBox/tree/master/src/test}{here}. 
The tests.js file contains the source code for all testing. The Test.html file 
contains the output of this code. All test were conducted using the third party 
testing software QUnit, outlined in the Design document.\\

Most of the unit testing was focused on ensuring the validity of the genetic 
algorithm and the car creation and manipulation elements of GrateBox, as 
graphical aspects of GrateBox proved far more difficult to test with unit 
testing.\\

Overall, these unit tests served to guarantee a level of functionality across 
builds, and did not account for non-functional requirements, as these were 
better suited to manual testing with user feedback.

\section{Changes Due to Testing}

Several changes were made to GrateBox as a result of testing. They have been 
divided below according to their related requirements. Many changes were made on 
a requirement by requirement basis, and these can be seen in sections 1 and 2 of 
this document.

\subsection{Changes to functional requirements}

Initial car design was predicated on the creation of vectors from a centre point 
and then the connecting of the end of these vectors to form a polygon that would 
serve as the body of the car. However, testing for car creation using this 
method proved prohibitively difficult. To this end, car bodies were redesigned 
to be composed of a series of conducted vertexes. This change also affected how 
car chromosomes were created and manipulated.\\

User surveys revealed the need for a pause button in GrateBox as users felt a 
lack of control over the program at times. This was added to the parameters 
section of GrateBox.\\

The initial values of the user variables (number of cars per generation, number 
of parents, and mutation rate) all increased as a result of user input. The 
initial values resulted in cars that were too slow in evolving, and would often 
require ten or more generations for a moderately successful car to emerge. 

\subsection{Changes to non-functional requirements}

User feedback told Grate that the UI of GrateBox was too minimal, and that look 
and feel requirements were not being met. To this end, an html visual enhancer, 
Bootstrap, was used to satisfy this user need. Users opinions' of GrateBox's 
look and feel increased dramatically following this change.\\

It was observed during user trials that many users had trouble grasping the 
exact nature of genetic algorithms quickly. To this end text was added to 
GrateBox to give users the most very basic background with which to use the 
program. It was important to Grate that this text not be overly extensive, as it 
was believed that this could go a long way to turning users off of our product. 
The exact amount and content of text was modified extensively over GrateBox's 
development cycle via user input.

\section{Automated Testing}

\subsection{Introduction to automated testing}

Automated testing proved difficult for certain elements of GrateBox, as it is 
by nature a visual product. Still some automated testing was conducted for the 
benefit of the testing team and to improve accuracy. QUnit, our unit testing 
software, allows for multiple executions of the same test with some variances, 
and this was done to ensure the soundness of many aspects of GrateBox. This 
functionality allows for the entrance of a variable into a field with the 
instructions to manipulate that variable within a range of possible values and 
determine many possible outputs (for example negative values, non-integer 
values, etc.). The genetic algorithm in particular benefited greatly from 
automated testing, as many different variables could be tested with minimal time 
investment. While it proved impractical for the project given time 
constrictions, further elaboration on GrateBox could utilise image analysing on 
a pixel by pixel basis to improve the quality of the graphical output. Although 
the overall value of such a time investment is questionable.\\

Outline below are all of our individual test cases, along with their names, 
initial states, inputs and expected outputs. A test was deemed to be successful 
if the expected output was the actual output. Only successful tests are listed 
here.

\subsection{Specific System Tests}

\begin{center}
\begin{longtable}{ l | p{10cm} }
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Mutation rate of 0\%\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre generated car generation and 0\% mutation rate\\
\textbf{Expected Output:} & The same generation as the input\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Mutation rate of 0\% leading to error\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre generated car generation and 0\% mutation rate with 
negative value for carsArray\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Selecting top three offspring with generation 
of three cars\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre generated car generation with input of 3 for 
selectNextGeneration\\
\textbf{Expected Output:} & Correct selection of top three cars\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Selecting top two offspring with generation of 
three cars\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre generated car generation with input of 2 for 
selectNextGeneration\\
\textbf{Expected Output:} & Correct selection of top two cars\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid selection of only one offspring for 
next generation with generation of three cars\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre generated car generation with input of 1 for 
selectNextGeneration\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid selection of no offspring for next 
generation with generation of three cars\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre generated car generation with input of 0 for 
selectNextGeneration\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid selection of negative offspring for 
next generation with generation of three cars\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre generated car generation with input of -1 for 
selectNextGeneration\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Selecting top three offspring with generation 
of four cars\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre generated car generation with input of 3 for 
selectNextGeneration\\
\textbf{Expected Output:} & Correct selection of top three cars\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid selection of five offspring for next 
generation with generation of four cars\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre generated car generation with input of 5 for 
selectNextGeneration\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid selection of no offspring for next 
generation with generation of four cars\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre generated car generation with input of 0 for 
selectNextGeneration\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid selection of negative offspring for 
next generation with generation of four cars\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre generated car generation with input of -1 for 
selectNextGeneration\\
\textbf{Expected Output:} & \\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Car generation with two valid wheels\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre determined random seed and run of standard car generation 
module\\
\textbf{Expected Output:} & Two valid wheel placements on a car\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Car generation with two valid wheel radii\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre determined random seed and run of standard car generation 
module\\
\textbf{Expected Output:} & Two valid wheel radius values on a car\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Car generation with vertex positions\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre determined random seed and run of standard car generation 
module\\
\textbf{Expected Output:} & Valid vertex creation and positions\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Car generation with vertex angles\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre determined random seed and run of standard car generation 
module\\
\textbf{Expected Output:} & Valid vertex angle creation and assignments\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid car generation with wheels\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre determined random seed and run of invalid car generation 
module\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid car generation with wheel radii\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre determined random seed and run of invalid car generation 
module\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid car generation with vertex positions\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre determined random seed and run of invalid car generation 
module\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid car generation with vertex angles\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Pre determined random seed and run of invalid car generation 
module\\
\textbf{Expected Output:} &Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Car chromosome return\\
\textbf{Initial State:} & Generation of cars generated\\
\textbf{Input:} & Chromosome generation module run\\
\textbf{Expected Output:} & Valid chromosome\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Car graphics\\
\textbf{Initial State:} & Pre generated car object\\
\textbf{Input:} & Car object run through graphics module\\
\textbf{Expected Output:} & Valid car generated as expected on screen\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid car graphics\\
\textbf{Initial State:} & Pre generated car object with inaccurate index 
values\\
\textbf{Input:} & Car object run through graphics module\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid car graphics 2\\
\textbf{Initial State:} & Pre generated car object with negative index values\\
\textbf{Input:} & Car object run through graphics module\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Road graphics\\
\textbf{Initial State:} & Pre generated road\\
\textbf{Input:} & Road put through graphics module\\
\textbf{Expected Output:} & Valid road created as expected on screen\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid road graphics\\
\textbf{Initial State:} & Pre generated road\\
\textbf{Input:} & Road put through graphics module\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Correct fitness values at locations\\
\textbf{Initial State:} & Generation of cars created and simulation run to 
determine fitness\\
\textbf{Input:} & Fitness value determination module run for series of car 
locations from simultation\\
\textbf{Expected Output:} & Valid corresponding fitness values\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid fitness values at locations\\
\textbf{Initial State:} & Generation of cars created and simulation run to 
determine fitness\\
\textbf{Input:} & Invalid fitness value determination module run for series of 
car locations from simulation\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Highest fitness value from fitness values\\
\textbf{Initial State:} & Generation of cars created and simulation run to 
determine fitness\\
\textbf{Input:} & Fitness value determination module run to determine highest 
fitness from several cars\\
\textbf{Expected Output:} & Highest fitness value from series of cars\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid highest fitness values\\
\textbf{Initial State:} & Generation of cars created and simulation run to 
determine fitness\\
\textbf{Input:} & Invalid fitness value determination module run to determine 
highest fitness from several cars\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Valid health of cars\\
\textbf{Initial State:} & Generation of cars created with pre set health 
values\\
\textbf{Input:} & Cars run through simulation\\
\textbf{Expected Output:} & Cars terminated when health reaches zero\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid health of cars\\
\textbf{Initial State:} & Generation of cars created with invalid pre set health 
values\\
\textbf{Input:} & Cars run through simulation\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Valid text to user display\\
\textbf{Initial State:} & Generation of cars created and simulation running\\
\textbf{Input:} & Chromosome and fitness modules commanded to send text to GUI\\
\textbf{Expected Output:} & GUI properly displays text and displayed text is 
valid\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Invalid text to user display\\
\textbf{Initial State:} & Generation of cars created and simulation running\\
\textbf{Input:} & Invalid chromosome and invalid fitness modules commanded to 
send text to GUI\\
\textbf{Expected Output:} & Error message displayed\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & User operability pre user guide\\
\textbf{Initial State:} & GrateBox not open or downloaded on machine\\
\textbf{Input:} & Users prompted to open GrateBox on their own without 
instructions\\
\textbf{Expected Output:} & User opens GrateBox on machine\\[0.6em]
\textbf{Result of Test:} & Fail\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & User operability post user guide\\
\textbf{Initial State:} & GrateBox not open or downloaded on machine\\
\textbf{Input:} & Users prompted to open GrateBox on their own without 
instructions but with user guide\\
\textbf{Expected Output:} & User opens GrateBox on machine\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & User task execution\\
\textbf{Initial State:} & GrateBox open on user\\
\textbf{Input:} & User prompted to complete arbitrary set of four tasks within 
one minute\\
\textbf{Expected Output:} & Task completion in alloted time frame\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Performance evaluation 1\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Simultaneous beginning of timer and execution of car 
generation, mutation, and display\\
\textbf{Expected Output:} & Valid execution of car generation, mutation, and 
display within 20 seconds\\[0.6em]
\textbf{Result of Test:} & Passed\\
\hline
\rule{0pt}{1.5em}\textbf{Name:} & Performance evaluation 2\\
\textbf{Initial State:} & None\\
\textbf{Input:} & Entrance of several randomly selected final numerical values 
from GrateBox\\
\textbf{Expected Output:} & Pre determined and hand calculated value match those 
randomly selected, validating GrateBox algorithms\\[0.6em]
\textbf{Result of Test:} & Passed\\
\end{longtable}
\end{center}

\section{Trace to Requirements}

The requirements are described in more detail in the SRS document. The tests are 
given by their abbreviated forms. For example GA refers to the Genetic Algorithm 
tests, which are described in more detail in the Test Plan document.
		
\begin{table}[H]
\centering
\begin{tabular}{p{0.2\textwidth} p{0.6\textwidth}}
\toprule
\textbf{Req.} & \textbf{Tests}\\
\midrule
Req 1: Car body parameters & CM \\
Req 2: Wheel number parameters & CM \\
Req 3: Wheel radius parameters & CM\\
Req 4: Wheel position parameters & CM\\
Req 5: Min weight parameters & CM\\
Req 6: Max weight parameters & CM\\
Req 7: Generation display parameters & GR\\
Req 8: Fitness display parameters & GA, FI\\
Req 9: Random seed parameters & GA\\
Req 10: Mutation rate parameters & GA\\
\bottomrule
\end{tabular}
\caption{Trace between functional requirements and tests (set 1)}
\label{TblRT}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{p{0.2\textwidth} p{0.6\textwidth}}
\toprule
\textbf{Req.} & \textbf{Tests}\\
\midrule
Req 11: Cars per generation parameters  & GA\\
Req 12: Road generation parameters & CM\\
Req 13: Min cars per generation parameters & CM\\
Req 14: Max cars per generation parameters & CM\\
Req 15: Top cars parameters & CM, FI\\
Req 16: Max top cars parameters & CM, GA, FI\\
Req 17: Min top cars parameters & CM, GA, FI\\
Req 18: Non-moving parameters & CM, GU\\
Req 19: Fitness parameters & FI\\
Req 20: Default value replacement parameters & GU\\
\bottomrule
\end{tabular}
\caption{Trace between functional requirements and tests (set 2)}
\label{TblRT2}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{p{0.2\textwidth} p{0.6\textwidth}}
\toprule
\textbf{Req.} & \textbf{Tests}\\
\midrule
Req 21: Appearance Parameters & LF\\
Req 22: Style Parameters & LF\\
Req 23: Ease of Use Parameters & US\\
Req 24: Personalization Parameters & LF\\
Req 25: Learning Parameters & US\\
Req 26: Speed and Latency Parameters & PF\\
Req 27: Precision and Reliability Parameters & PF\\
Req 28: Longevity Parameters & PF\\
\bottomrule
\end{tabular}
\caption{Trace between non-functional requirements and tests}
\label{TblRT2}
\end{table}

\section{Trace to Modules}	

For reference, the modules are as follows. There are displayed with more detail 
in the Design document. All tests are referred to in their abbreviated form. For 
example Genetic Algorithm tests are referred to by the short form GA. These are 
elaborated on in the Test Plan document.

\begin{description}
\item [\refstepcounter{mnum} \mthemnum \label{mHardware}:] Hardware hiding 
module
\item [\refstepcounter{mnum} \mthemnum \label{mCreateCar}:]  Car creation 
module. Tested with the CM tests.
\item [\refstepcounter{mnum} \mthemnum \label{mEvolveCar}:] Evolve car module. 
Tested with the CM tests.
\item [\refstepcounter{mnum} \mthemnum \label{mCreateRoad}:] Road creation 
module. Tested with the CM tests.
\item [\refstepcounter{mnum} \mthemnum \label{mGraphicsDisplay}:] Graphics 
display module. Tested with the GR and GU tests.
\item [\refstepcounter{mnum} \mthemnum \label{mGeneticAlgorithm}:] Genetic 
Algorithm module. Tested with the GA tests.
\item [\refstepcounter{mnum} \mthemnum \label{mRandomSeed}:] Random seed 
generation and manipulation module. Tested with the GA tests.
\item [\refstepcounter{mnum} \mthemnum \label{mFitness}:] Fitness determination 
module. Tested with the FI tests.
\item [\refstepcounter{mnum} \mthemnum \label{mSearching}:] Searching algorithms 
module. Tested with the GA tests.
\item [\refstepcounter{mnum} \mthemnum \label{mSorting}:] Sorting algorithms 
module. Tested with the GA tests.
\item [\refstepcounter{mnum} \mthemnum \label{mPopulationGeneration}:] 
Population generation algorithms module. Tested with the GA tests.
\end{description}


\section{Code Coverage Metrics}

In the Test Plan document, Grate endeavoured to achieve 70\% coverage with our 
automated and unit testing. While not every unit test possible was executed, 
most were, and Grate feels that this coverage metric was reached, as a large 
majority of our actual code contains corresponding tests to validate it. \\

The modularized nature of our code reduced the overall usefulness of larger 
coverage 
tests. For example, the inclusion of the genetic algorithm in a test for 
graphical validity achieves very little, as the modularized nature of the code 
requires little to no interaction between these two modules.\\

It is harder to define coverage for non-functional testing; however Grate has 
undertaken great efforts through surveys and manual testing to guarantee the 
most complete product possible in terms of look and feel, usability, and 
robustness. And as seen in section 2 of this document,  the metrics we set out 
to reach have been achieved.
\end{document}


